### 2018-02-13 publications.tex
Update in Feb 2018

\section{Publications}

\subsection{Refereed Publications
  \href{http://adsabs.harvard.edu/cgi-bin/nph-abs_connect?library&libname=Jeong-Gyu+Kim&libid=4b3ebd59ff}{\color{dodgerblue}{(ADS Link)}}}

\begin{benumerate}{6}
\item \textit{Modeling Radiative Feedback from Massive Stars: I.
  Implementation of Adaptive Ray Tracing Method and Tests}\\
\textbf{Kim, J.-G.}, Kim, W.-T., Ostriker, E. C.,\& Skinner A. M.
2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
  Regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts
  Surrounding H II regions}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral
  Shocks}\\
Kim, W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the
  Interstellar Medium}\\
\textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating,
    Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification}\\
  \textbf{Kim, J.-G.}, Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012,
  ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Modeling Radiative Feedback from Massive Stars: II.
    Dispersal of Giant Molecular Clouds by Photoionization and
    Radiation Pressure} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
    prep}
\item[] \textit{Modeling Radiative Feedback from Massive Stars: III.
    Escape of Radiation} \\
  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
    prep}
% \item[] \textit{Modeling Radiative Feedback from Massive Stars:
%     IV. Comparison of Star Formation Efficiencies in Observed and
%     Simulated Giant Molecular Clouds}\\
%   \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. \textit{2018, in
%     prep}
% \item[] \textit{Heating and Ionization of
%       the Diffuse Interstellar Medium by UV Radiation in TIGRESS}\\
%     \textbf{Kim, J.-G.}, Kim, C.-G., Seon K.-I., Ostriker, E. C., \&
%     Kim, W.-T. \textit{2018, in prep}
\end{enumerate}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2018-02-24 publications.tex
Added Osaka, AAS presentations.
Update publication. Science paper ApJ submitted.

@@
 
-\begin{benumerate}{6}
+\begin{benumerate}{7}
+\item \textit{Modeling Radiative Feedback from Massive Stars: II.
+    Dispersal of Star-Forming Giant Molecular Clouds by
+    Photoionization and Radiation Pressure} \\
+  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018,
+  \textit{submitted to ApJ}
 \item \textit{Modeling Radiative Feedback from Massive Stars: I.
@@
     Pressure-Confined,
-    Polytropic Gas Disks with Vertical Stratification}\\
+    Polytropic Gas Disks with Vertical Stratification} \\
   \textbf{Kim, J.-G.}, Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012,
@@
 \begin{enumerate}
-\item[] \textit{Modeling Radiative Feedback from Massive Stars: II.
-    Dispersal of Giant Molecular Clouds by Photoionization and
-    Radiation Pressure} \\
-  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
-    prep}
 \item[] \textit{Modeling Radiative Feedback from Massive Stars: III.
-    Escape of Radiation} \\
+    Escape of Ionizing and Non-ionizing Radiation from Star-Forming
+    Giant Molecular Clouds} \\
   \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in

### 2019-06-03 publications.tex
Paper II accepted.
Update several files.

--- 2018-02-13 publications.tex
@@
 
-\subsection{Refereed Publications
-  \href{http://adsabs.harvard.edu/cgi-bin/nph-abs_connect?library&libname=Jeong-Gyu+Kim&libid=4b3ebd59ff}{\color{dodgerblue}{(ADS Link)}}}
+\subsection{Refereed Publications}
 
-\begin{benumerate}{6}
-\item \textit{Modeling Radiative Feedback from Massive Stars: I.
-  Implementation of Adaptive Ray Tracing Method and Tests}\\
-\textbf{Kim, J.-G.}, Kim, W.-T., Ostriker, E. C.,\& Skinner A. M.
-2017, ApJ, 851, 93
+\href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{(ADS
+Link)}}
+
+\begin{benumerate}{7}
+\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
+of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
+Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
+68
+\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
+Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
+Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
 \item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
-  Regions}\\
-\textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
+Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
 137
-\item \textit{Instability of Magnetized Ionization Fronts
-  Surrounding H II regions}\\
-\textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
-\item \textit{Nature of Wiggle Instability of Galactic Spiral
-  Shocks}\\
-Kim, W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
-\item \textit{Instability of Evaporation Fronts in the
-  Interstellar Medium}\\
+\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
+regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
+\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
+W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
+\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
   \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
-\item \textit{Gravitational Instability of Rotating,
-    Pressure-Confined,
-    Polytropic Gas Disks with Vertical Stratification}\\
-  \textbf{Kim, J.-G.}, Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012,
-  ApJ, 761, 131
+\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
+    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
+  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
 \end{benumerate}
@@
 \begin{enumerate}
-\item[] \textit{Modeling Radiative Feedback from Massive Stars: II.
-    Dispersal of Giant Molecular Clouds by Photoionization and
-    Radiation Pressure} \\
-  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
+\item[] \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
+    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
+    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ submitted}
+\item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
+    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
+  Ostriker, E. C. \textit{2019, in prep}
+\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\ Kado
+  Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C. \textit{2019, in
     prep}
-\item[] \textit{Modeling Radiative Feedback from Massive Stars: III.
-    Escape of Radiation} \\
-  \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, \textit{in
-    prep}
-% \item[] \textit{Modeling Radiative Feedback from Massive Stars:
-%     IV. Comparison of Star Formation Efficiencies in Observed and
-%     Simulated Giant Molecular Clouds}\\
-%   \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. \textit{2018, in
-%     prep}
-% \item[] \textit{Heating and Ionization of
-%       the Diffuse Interstellar Medium by UV Radiation in TIGRESS}\\
-%     \textbf{Kim, J.-G.}, Kim, C.-G., Seon K.-I., Ostriker, E. C., \&
-%     Kim, W.-T. \textit{2018, in prep}
 \end{enumerate}
 
-%%% Local Variables:
-%%% mode: latex
-%%% TeX-master: t
-%%% End:
+%%% Local Variables: %%% mode: latex %%% TeX-master: t %%% End:

### 2019-08-31 publications.tex
Escape of radiation accepted.

@@
 
-\subsection{Refereed Publications}
+\subsection{Refereed Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
+Search}}}
 
-\href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{(ADS
-Link)}}
-
-\begin{benumerate}{7}
+\begin{benumerate}{8}
+\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
+    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
+    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ accepted}
 \item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
@@
 \begin{enumerate}
-\item[] \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
-    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
-    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ submitted}
+\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\
+  Kado-Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C.
+  \textit{2019, to be submitted}
 \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
@@
   Ostriker, E. C. \textit{2019, in prep}
-\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\ Kado
-  Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C. \textit{2019, in
-    prep}
+\item[] \textit{TIGRESS-RT: Implementation New Heating/Cooling Module with
+    Adaptive Ray Tracing}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
+  Ostriker, E. C.
 \end{enumerate}

### 2020-10-28 publications.tex
Update in October 2020

@@
 
-\begin{benumerate}{8}
+*Authored by students under direct supervision
+
+\begin{benumerate}{11}
+\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
+    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
+    J.-G.}, \textit{ApJ accepted}
+\item \textit{Factories of CO-dark gas: molecular clouds with limited star
+formation efficiencies by far-ultraviolet feedback} \\
+  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
+  497, 5061I
+\item \textit{Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
+    Galactic Disks}\\
+  $^{*}$Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
+  897, 143
 \item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
     of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
-    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, \textit{ApJ accepted}
+    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
 \item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
@@
 \begin{enumerate}
-\item[] \textit{Diffuse Ionized Gas in TIGRESS Simulations of the ISM}\\
-  Kado-Fong, E., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E. C.
-  \textit{2019, to be submitted}
-\item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
-    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
-  Ostriker, E. C. \textit{2019, in prep}
-\item[] \textit{TIGRESS-RT: Implementation New Heating/Cooling Module with
-    Adaptive Ray Tracing}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
-  Ostriker, E. C.
+\item[] \textit{Dispersal of Star-Forming Molecular Clouds by UV Radiation
+    Feedback: Dependence on Gravitational Boundedness and Magnetic Fields} \\
+  \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. \textit{2020, to be
+    submitted}
+\item[] \textit{Implementation of a Cooling Module for the ISM Coupled with Radiative
+    Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C.
+  \textit{2020, to be submitted}
+\item[] \textit{A Theory of Stellar Wind Bubble Expansion in the Turbulent
+    ISM}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
+  \textit{2020, in preparation}
+\item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
+    of M15} \\
+  Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{2021,
+    in preparation}
+
+  % \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
+%     Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
+%   Ostriker, E. C. \textit{2019, in prep}
 \end{enumerate}

### 2020-11-24 publications.tex
Update publication

@@
 
-\subsection{Refereed Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
+\subsection{Journal Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
 Search}}}
 
-*Authored by students under direct supervision
+*Led by a student under direct supervision
 
-\begin{benumerate}{11}
+\begin{benumerate}{12}
+\item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
+    Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
+    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. arxiv:2011.07772 \textit{(submitted to
+    ApJ 10/2020)}
 \item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
     factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
-    J.-G.}, \textit{ApJ accepted}
+    J.-G.} 2020, ApJ, 903, 142 
 \item \textit{Factories of CO-dark gas: molecular clouds with limited star
@@
   497, 5061I
-\item \textit{Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
+\item \textit{$^{*}$Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
     Galactic Disks}\\
-  $^{*}$Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
+  Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
   897, 143
@@
 \begin{enumerate}
-\item[] \textit{Dispersal of Star-Forming Molecular Clouds by UV Radiation
-    Feedback: Dependence on Gravitational Boundedness and Magnetic Fields} \\
-  \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. \textit{2020, to be
-    submitted}
-\item[] \textit{Implementation of a Cooling Module for the ISM Coupled with Radiative
-    Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C.
-  \textit{2020, to be submitted}
-\item[] \textit{A Theory of Stellar Wind Bubble Expansion in the Turbulent
-    ISM}\\
+\item[] \textit{Implementation of a Module for Heating and Cooling in the ISM
+    Coupled with Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim,
+  C.-G., \& Ostriker, E. C. \textit{2020, in preparation}
+\item[] \textit{Molecular Cloud Destruction Controlled by Radiation, Winds, and
+Supernovae Feedback} \\ \textbf{Kim, J.-G.}, Lancaster, L., Kim, C.-G., \&
+Ostriker, E. C. \textit{2021, in preparation}
+\item[] \textit{Stellar Wind Bubbles in Turbulent Clouds:
+A Fractal Theory Validated with Hydrodynamic Simulations}\\
   Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
-  \textit{2020, in preparation}
+  \textit{2020, to be submitted 12/2020}
 \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case

### 2020-12-25 publications.tex
Updated publication. Mark important publications.

@@
 
-*Led by a student under direct supervision
+** Most important publications ; \# Led by a student under direct supervision
 
-\begin{benumerate}{12}
-\item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
+\begin{benumerate}{13}
+\item \textit{Stellar Wind Bubbles in Turbulent Clouds:
+A Fractal Theory Validated with Hydrodynamic Simulations}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
+  \textit{submitted to ApJ 12/2020}
+\item \textit{** Star Formation Efficiency and Dispersal of Giant Molecular
     Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
@@
   497, 5061I
-\item \textit{$^{*}$Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
+\item \textit{\# Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
     Galactic Disks}\\
@@
     J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
-\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
+\item \textit{** Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
 of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
@@
     Coupled with Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim,
-  C.-G., \& Ostriker, E. C. \textit{2020, in preparation}
+  C.-G., \& Ostriker, E. C. \textit{2021, in preparation}
 \item[] \textit{Molecular Cloud Destruction Controlled by Radiation, Winds, and
@@
 Ostriker, E. C. \textit{2021, in preparation}
-\item[] \textit{Stellar Wind Bubbles in Turbulent Clouds:
-A Fractal Theory Validated with Hydrodynamic Simulations}\\
-  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
-  \textit{2020, to be submitted 12/2020}
 \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case

### 2021-02-22 publications.tex
GMC-AB ApJ accepted

@@
 
-\begin{benumerate}{13}
-\item \textit{Stellar Wind Bubbles in Turbulent Clouds:
-A Fractal Theory Validated with Hydrodynamic Simulations}\\
+\begin{benumerate}{14}
+\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
+II. Numerical Simulations and Theory Compared}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
+  \textit{submitted to ApJ 12/2020}
+\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
+I. Theory and Applications to Star-Forming Clouds}\\
   Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
@@
     Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
-    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. arxiv:2011.07772 \textit{(submitted to
-    ApJ 10/2020)}
+    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova,
+  N. arxiv:2011.07772 \textit{ApJ accepted}
 \item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion

### 2022-04-11 publications.tex
Wind papers accepted
Add SFR MW paper

--- 2020-11-24 publications.tex
@@
 
-*Led by a student under direct supervision
+% ** Important publications ;
 
-\begin{benumerate}{12}
+\# Led by a student under direct supervision
+
+\begin{benumerate}{16}
+\item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
+  Evans, Neal J., II, \textbf{Kim, J.-G.}, \& Ostriker, E. C. 2022, ApJL in
+  press
+\item \textit{Star Formation Regulation and Self-Pollution by Stellar Wind
+    Feedback}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJL,
+  922, 3L
+\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
+    II. Validation of Theory with Hydrodynamic Simulations}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJ,
+  914, 90L
+\item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
+I. Fractal Theory and Application to Star-Forming Clouds}\\
+  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G., 2021, ApJ,
+914, 89L
 \item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
     Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
-    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. arxiv:2011.07772 \textit{(submitted to
-    ApJ 10/2020)}
+    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova,
+  N. 2021, ApJ, 911, 128K
 \item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
@@
 
-\subsection{Papers in Preparation}
-\begin{enumerate}
-\item[] \textit{Implementation of a Module for Heating and Cooling in the ISM
-    Coupled with Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim,
-  C.-G., \& Ostriker, E. C. \textit{2020, in preparation}
-\item[] \textit{Molecular Cloud Destruction Controlled by Radiation, Winds, and
-Supernovae Feedback} \\ \textbf{Kim, J.-G.}, Lancaster, L., Kim, C.-G., \&
-Ostriker, E. C. \textit{2021, in preparation}
-\item[] \textit{Stellar Wind Bubbles in Turbulent Clouds:
-A Fractal Theory Validated with Hydrodynamic Simulations}\\
-  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
-  \textit{2020, to be submitted 12/2020}
-\item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
-    of M15} \\
-  Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{2021,
-    in preparation}
-
+% \subsection{Papers in Preparation}
+% \begin{enumerate}
+% \item[] \textit{Modeling Thermochemistry of the Interstellar Medium Coupled with
+%     UV Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
+%   Ostriker, E. C. \textit{2021, in preparation}
+% \item[] \textit{Radiation Magnetohydrodynamic Simulations of Molecular Cloud
+%     Destruction: I. Relative Importance of Radiation, Winds, and Supernovae} \\
+%   \textbf{Kim, J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C.
+%   \textit{in preparation}
+% \item[] \textit{Star Formation Simulations Applied to the Milky Way and Other
+%     Galaxies}\\ \textbf{Kim, J.-G.}, Evans, N. J., II, \& Ostriker, E. C.
+%   \textit{in preparation}
+% \item[] \textit{Which physics/feedback control star formation rates and galactic
+%     wind launching conditions: a view from TIGRESS} \\ Kim, C.-G., \textbf{Kim,
+%     J.-G.}, Ostriker, E. C., Gong, M. \textit{in preparation}
+% \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
+%     of M15} \\
+%   Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{
+%     in preparation}
 %  \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
@@
 %   Ostriker, E. C. \textit{2019, in prep}
-\end{enumerate}
+% \end{enumerate}
 

### 2022-05-07 publications.tex
Updated

@@
 \item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
-  Evans, Neal J., II, \textbf{Kim, J.-G.}, \& Ostriker, E. C. 2022, ApJL in
-  press
+  Evans, Neal J., II, \textbf{Kim, J.-G.}, \& Ostriker, E. C. 2022, ApJL, 929L,
+  18E
 \item \textit{Star Formation Regulation and Self-Pollution by Stellar Wind
@@
   Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. 2021, ApJL,
-  922, 3L
+  922L, 3L
 \item \textit{Efficiently Cooled Stellar Wind Bubbles in Turbulent Clouds:
@@
 
-% \subsection{Papers in Preparation}
-% \begin{enumerate}
-% \item[] \textit{Modeling Thermochemistry of the Interstellar Medium Coupled with
-%     UV Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \&
-%   Ostriker, E. C. \textit{2021, in preparation}
-% \item[] \textit{Radiation Magnetohydrodynamic Simulations of Molecular Cloud
-%     Destruction: I. Relative Importance of Radiation, Winds, and Supernovae} \\
-%   \textbf{Kim, J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C.
-%   \textit{in preparation}
-% \item[] \textit{Star Formation Simulations Applied to the Milky Way and Other
-%     Galaxies}\\ \textbf{Kim, J.-G.}, Evans, N. J., II, \& Ostriker, E. C.
-%   \textit{in preparation}
-% \item[] \textit{Which physics/feedback control star formation rates and galactic
-%     wind launching conditions: a view from TIGRESS} \\ Kim, C.-G., \textbf{Kim,
-%     J.-G.}, Ostriker, E. C., Gong, M. \textit{in preparation}
+\subsection{Papers in Preparation}
+\begin{enumerate}
+\item[] \textit{Photochemistry and Heating/Cooling of the Multiphase
+    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
+  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{2022, to be submitted}
+\item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
+    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., Ostriker,
+  E. C. \textit{2022, to be submitted}
+\item[] \textit{Destruction of Giant Molecular Clouds by Stellar Feedback: I.
+    Relative Importance of Radiation, Winds, and Supernovae} \\ \textbf{Kim,
+    J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C. \textit{2022, in
+    prep.}
+\item[] \textit{The Lyman Continuum and Far-UV Interstellar Radiation Field in
+    Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
+  \textbf{Kim, J-.G.}, Ostriker, E. C., Kim, C.-G. \textit{2022, in prep.}
+\item[] \textit{Bubble Expansion Driven by Stellar Winds and Radiation in
+    Turbulent, Magnetized Clouds} \\ Lancaster, L., Ostriker, E. C.,
+  \textbf{Kim, J.-G.}, Kim, C.-G. \textit{2022, in prep.}
+\item[] \textit{Modeling Polarized Thermal Emission from Dust Grains in Low-Mass
+    Protostellar Cores with POLARIS} \\ Giang, N. C., Hoang, T., \& \textbf{Kim,
+    J.-G.} \textit{2022, in prep.}
 % \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
 %     of M15} \\
-%   Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{
-%     in preparation}
+%   Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{in prep.}
  % \item[] \textit{Recovery of Cloud-Scale Star Formation Rate Based on Ionizing
  %    Luminosity: Calibration for Escape of Radiation} \\ \textbf{Kim, J.-G.} \&
-%   Ostriker, E. C. \textit{2019, in prep}
-% \end{enumerate}
+ %  Ostriker, E. C. \textit{in prep.}
+\end{enumerate}
 

### 2022-06-21 publications.tex
Newcool paper submitted

@@
 
-\begin{benumerate}{16}
+\begin{benumerate}{17}
+\item \textit{Photochemistry and Heating/Cooling of the Multiphase
+    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
+  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{ApJ submitted}
 \item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
@@
 \begin{enumerate}
-\item[] \textit{Photochemistry and Heating/Cooling of the Multiphase
-    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
-  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{2022, to be submitted}
 \item[] \textit{What Regulates Galactic Star Formation Rates? A View from New

### 2022-10-08 publications.tex
Moved to NAOJ. Submitted MNRAS paper.

--- 2022-05-07 publications.tex
@@
 
-\begin{benumerate}{16}
+\begin{benumerate}{18}
+\item \textit{Physical Modeling of Dust Polarization from Magnetically
+Enhanced Radiative Torque (MRAT) Alignment in Protostellar Cores with POLARIS}
+\\ Giang, N. C., Hoang, T., \textbf{Kim, J.-G.}, \& Tram, L. N. \textit{2022,
+MNRAS submitted}
+\item \textit{Photochemistry and Heating/Cooling of the Multiphase Interstellar
+Medium with UV Radiative Transfer in Magnetohydrodynamic Simulations} \\
+\textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C., \textit{ApJS
+submitted}
 \item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
@@
 \begin{enumerate}
-\item[] \textit{Photochemistry and Heating/Cooling of the Multiphase
-    Interstellar Medium with UV Radiative Transfer} \\ \textbf{Kim, J.-G.},
-  Gong, M., Kim, C.-G., \& Ostriker, E. C. \textit{2022, to be submitted}
 \item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
-    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., Ostriker,
+    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., \& Ostriker,
   E. C. \textit{2022, to be submitted}
@@
     Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
-  \textbf{Kim, J-.G.}, Ostriker, E. C., Kim, C.-G. \textit{2022, in prep.}
-\item[] \textit{Bubble Expansion Driven by Stellar Winds and Radiation in
-    Turbulent, Magnetized Clouds} \\ Lancaster, L., Ostriker, E. C.,
-  \textbf{Kim, J.-G.}, Kim, C.-G. \textit{2022, in prep.}
-\item[] \textit{Modeling Polarized Thermal Emission from Dust Grains in Low-Mass
-    Protostellar Cores with POLARIS} \\ Giang, N. C., Hoang, T., \& \textbf{Kim,
-    J.-G.} \textit{2022, in prep.}
+  Ostriker, E. C., \textbf{Kim, J-.G.}, \& Kim, C.-G. \textit{2022, in prep.}
+\item[] \textit{The Effects of Magnetic Fields and H II regions on the Dynamics
+of Stellar Wind Bubbles} \\ Lancaster, L., Ostriker, E. C.,
+  \textbf{Kim, J.-G.}, \& Kim, C.-G. \textit{2022, in prep.}
 % \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case

### 2023-05-25 publications.tex
Update of talks

@@
 
-\begin{benumerate}{18}
-\item \textit{Physical Modeling of Dust Polarization from Magnetically
-Enhanced Radiative Torque (MRAT) Alignment in Protostellar Cores with POLARIS}
-\\ Giang, N. C., Hoang, T., \textbf{Kim, J.-G.}, \& Tram, L. N. \textit{2022,
-MNRAS submitted}
+\begin{benumerate}{20}
+\item \textit{Implementation of Chemistry in the Athena++ Code} \\ Gong, M. et al. (incl.
+\textbf{JGK}), ApJ submitted
+\item \textit{Physical Modeling of Dust Polarization from Magnetically Enhanced Radiative
+    Torque (MRAT) Alignment in Protostellar Cores with POLARIS} \\ Giang, N. C., Hoang,
+  T., \textbf{Kim, J.-G.}, \& Tram, L. N. 2023, MNRAS, 520, 3788
+\item \textit{Introducing TIGRESS-NCR: I. Co-regulation of Multiphase ISM and
+Star Formation Rates} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., \& Ostriker,
+E. C. 2023, ApJ, 946, 3
 \item \textit{Photochemistry and Heating/Cooling of the Multiphase Interstellar
 Medium with UV Radiative Transfer in Magnetohydrodynamic Simulations} \\
-\textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C., \textit{ApJS
-submitted}
+\textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C. 2023, ApJS, 264, 10
 \item \textit{Slow Star Formation in the Milky Way: Theory Meets Observations}\\
@@
 
-\subsection{Papers in Preparation}
-\begin{enumerate}
-\item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
-    TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., \& Ostriker,
-  E. C. \textit{2022, to be submitted}
-\item[] \textit{Destruction of Giant Molecular Clouds by Stellar Feedback: I.
-    Relative Importance of Radiation, Winds, and Supernovae} \\ \textbf{Kim,
-    J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C. \textit{2022, in
-    prep.}
-\item[] \textit{The Lyman Continuum and Far-UV Interstellar Radiation Field in
-    Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
-  Ostriker, E. C., \textbf{Kim, J-.G.}, \& Kim, C.-G. \textit{2022, in prep.}
-\item[] \textit{The Effects of Magnetic Fields and H II regions on the Dynamics
-of Stellar Wind Bubbles} \\ Lancaster, L., Ostriker, E. C.,
-  \textbf{Kim, J.-G.}, \& Kim, C.-G. \textit{2022, in prep.}
+% \subsection{Papers in Preparation}
+% \begin{enumerate}
+% \item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
+%     TIGRESS Simulations} \\ Kim, C.-G., \textbf{Kim, J.-G.}, Gong, M., \& Ostriker,
+%   E. C. \textit{2022, to be submitted}
+% \item[] \textit{Destruction of Giant Molecular Clouds by Stellar Feedback: I.
+%     Relative Importance of Radiation, Winds, and Supernovae} \\ \textbf{Kim,
+%     J.-G.}, Lancaster, L., Kim, C.-G., \& Ostriker, E. C. \textit{2022, in
+%     prep.}
+% \item[] \textit{The Lyman Continuum and Far-UV Interstellar Radiation Field in
+%     Simulations of Multiphase, Star-forming Galactic Disks} \\ Linzer, N.,
+%   Ostriker, E. C., \textbf{Kim, J-.G.}, \& Kim, C.-G. \textit{2022, in prep.}
+% \item[] \textit{The Effects of Magnetic Fields and H II regions on the Dynamics
+% of Stellar Wind Bubbles} \\ Lancaster, L., Ostriker, E. C.,
+%   \textbf{Kim, J.-G.}, \& Kim, C.-G. \textit{2022, in prep.}
 % \item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
@@
  %  Ostriker, E. C. \textit{in prep.}
-\end{enumerate}
+%\end{enumerate}
 

### 2023-12-22 publications.tex
Update 12/2023

@@
 \item \textit{Implementation of Chemistry in the Athena++ Code} \\ Gong, M. et al. (incl.
-\textbf{JGK}), ApJ submitted
+\textbf{JGK}), 2023, ApJS, 268, 42
 \item \textit{Physical Modeling of Dust Polarization from Magnetically Enhanced Radiative
@@
 
-% \subsection{Papers in Preparation}
-% \begin{enumerate}
+\subsection{Papers in Preparation}
+\begin{enumerate}
+\item[] \textit{Structure and Dynamics of Density-Bounded H II Regions with Photoevaporative Outflows} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., Lancaster, L., \& Kim, C.-G. \textit{2024, in prep.}
+\item[] \textit{The Geometric and Numerical Roots of Cooling and Dynamics in Simulated Wind-Blown Bubbles} \\ Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. \textit{2024, in prep.}
+\item[] \textit{UV Radiation Fields in Star-Forming Disk Galaxies: Numerical Simulations with TIGRESS-NCR} \\ Linzer, N., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G. \textit{2024, in prep.}
+\item[] \textit{TIGERSS-NCR: Low Metallicity Simulation Suite} \\ Kim, C.-G., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Gong, M. \textit{2024, in prep.}
   % \item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
@@
  %  Ostriker, E. C. \textit{in prep.}
-%\end{enumerate}
+\end{enumerate}
 

### 2024-07-17 publications.tex
Update

--- 2023-05-25 publications.tex
@@
 
-\begin{benumerate}{20}
+\begin{benumerate}{22}
+\item \textit{Metallicity Dependence of Pressure-Regulated Feedback-Modulated Star Formation in the TIGRESS-NCR Simulation Suite} \\ Kim, C.-G., Ostriker, E.
+C., \textbf{Kim, J.-G.}, Gong, M., \& LtU collaboration \textit{2024, ApJ accepted}
+\item \textit{Geometry, Dissipation, Cooling, and the Dynamical Evolution of Wind-Blown Bubbles} \\ Lancaster, L., Ostriker, E.
+C., Kim, C.-G., \textbf{Kim, J.-G.}, \& Bryan, G.
+\textit{2024, ApJ, 970, 18}
 \item \textit{Implementation of Chemistry in the Athena++ Code} \\ Gong, M. et al. (incl.
-\textbf{JGK}), ApJ submitted
+\textbf{JGK}), 2023, ApJS, 268, 42
 \item \textit{Physical Modeling of Dust Polarization from Magnetically Enhanced Radiative
@@
 
-% \subsection{Papers in Preparation}
-% \begin{enumerate}
+\subsection{Papers in Preparation}
+\begin{enumerate}
+\item[] \textit{Structure and Dynamics of Density-Bounded H II Regions with Photoevaporative Outflows} \\ \textbf{Kim, J.-G.}, Ostriker, E.
+C., Lancaster, L., \& Kim, C.-G.
+\textit{2024, in preparation}
+\item[] \textit{Ultraviolet Radiation Fields in Star-Forming Disk Galaxies: Numerical Simulations with TIGRESS-NCR} \\ Linzer, N., \textbf{Kim, J.-G.}, Kim, C.-G., \& Ostriker, E.
+C.
+\textit{2024, ApJ submitted}
+
 % \item[] \textit{What Regulates Galactic Star Formation Rates? A View from New
